---
title: "Fall 2026 Exploratory Data Analysis with R"
subtitle: "Lecture 1: Introduction to R"
author: "Mark Jensen"
institute: "Federal Reserve Bank of Atlanta"
date: "August 28, 2026"
format:
  academic-typst: 
    keep-typ: false
    extract-media: ''
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(gt)
exercise_number <- 0

unemp_df <- read_csv("data/unemployment.csv", col_types = cols(.default = col_double()))

```

# Course Logistics

```{r child = "slides/big_picture.qmd"}
```

```{r child = "slides/course_logistics.qmd"}
```

# Getting Started

```{r child = "slides/goals_for_today.qmd"}
```

```{r child = "slides/what-is-rstudio.qmd"}
```

```{r child = "slides/create-rstudio-cloud-account.qmd"}
```

```{r child = "slides/rstudio-cloud-interface.qmd"}
```

```{r child = "slides/rstudio-interface.qmd"}
```

```{r child = "slides/breakout-session1.qmd"}
```

# Import Data

```{r child = "slides/directory-setup-exercise1.qmd"}
```

```{r child = "slides/packages.qmd"}
```


```{r child = "slides/comment-syntax-example.qmd"}
```

```{r child = "slides/directory-setup-exercise3.qmd"}
```

```{r child = "slides/break1.qmd"}
```

```{r child = "slides/after-break1.qmd"}
```

```{r child = "slides/functions-intro.qmd"}
```

```{r child = "slides/mini-recap.qmd"}
```

```{r child = "slides/help.qmd"}
```

```{r child = "slides/what-is-in-the-data.qmd"}
```

```{r child = "slides/data-types.qmd"}
```

# Summarizing Data

```{r child = "slides/summarizing-data.qmd"}
```

```{r }
exercise_number <- exercise_number + 1
```

## Exercise `r exercise_number`: Analyze data

Compare two time periods

1. Compute mean unemployment for the time period 1980 - 1999
2. Compute mean unemployment for the time period 2000 - 2019
3. Calculate the difference. Discuss the results: 
    * Economic significance?
    * Possible explanations?
    * Statistical significance? More about this later in the course.


```{r child = "slides/break2.qmd"}
```


# Visualizing Data

```{r child = "slides/visualizing-data.qmd"}
```

```{r child = "slides/example-data.qmd"}
```

```{r child = "slides/example-plot.qmd"}
```

```{r child = "slides/du_bois_dataviz.qmd"}
```


# Recap

```{r child = "slides/recap.qmd"}
```

```{r child = "slides/links.qmd"}
```
