---
title: "Project Update 5"
subtitle: "ECON 345"
author: "Your Name"
date: "Due: 11:59PM October 17, 2026"
output: pdf_document
urlcolor: blue
---

**For Part A, you need to reproduce your work from Project Update 4 with revisions based on feedback you received. If you did not receive any feedback for a particular item, you should still include that item.**

# Part A - Iterating on Previous Work (30 points)

1. **Research Question (10)**

    - What is your research question? (2)

        - Answer:

    - How has your research question changed over the course of the project? (2)

        - Answer:

    - What are the key relationships in your data that could inform the answer to your research question? (2)

        - Answer:

    - Based on your data, what is a testable hypothesis for your research question? (4)

        - Answer:

2. **Summary Statistics (4)**

```{r, eval = TRUE, echo = FALSE}
# generate summary statistics, incorporating weights if applicable, using vtable or kable

```

    - Feedback incorporated, or struggles/no feedback to report: (2)

        - Answer:

3. **Conditional Summary Statistics (4)**

```{r, eval = TRUE, echo = FALSE}
# generate conditional summary statistics, incorporating weights if applicable, using vtable or kable

```

    - Feedback incorporated, or struggles/no feedback to report: (2)

        - Answer:

4. **Data Visualization (12)**

```{r, eval = TRUE, echo = FALSE}
# chart 1

# chart 2

# chart 3

```

    - What story does each chart tell? (5)

        - Answer:

    - Feedback incorporated, or struggles/no feedback to report: (2)

        - Answer:

# Part B - Refining Your Interpretation (30 points)

5. What did you originally expect to find in the data about the relationship between your key variables? (5)

    - Answer:

6. How have your findings differed from your original expectations? (5)

    - Answer:

7. How does your analysis thus far help inform your research question? Tell us a story. (10)

    - Answer:

8. What limitations exist to your analysis and visualizations so far? How could you overcome these limitations? (10)

    - Answer:

# Part C - Analysis With a T-Test (20 points)

9. Define a grouping variable based on your independent variable that splits your data into two groups. Explain your reasoning. (5)

    - Answer:

10. Based on your summary statistics or histogram, describe the relationship between your dependent and independent variables. (5)

    - Answer:

11. Which test are you using?

    - One-sample or two-sample? One-sided or two-sided? (2)

        - Answer:

    - State your null and alternative hypotheses. (3)

        - Answer:

12. Run the t-test with `infer::t_test()` and interpret the results. (5)

```{r, eval = TRUE, echo = FALSE}
# library(infer)
# t_test(your_data, response = your_response, explanatory = your_grouping_variable)

```

    - Interpretation:

        - Answer:

# Part D - Follow-up With Your Adviser (10 points)

13. Email your adviser with your knitted output, with `econ345.spelman@gmail.com` cc'd. (5)

    - Summary of what you've done this week and what you've learned: (5)

        - Answer:

# Part E - Share With Your Classmates (10 points)

14. Pick one chart from Part A and share it on the Canvas discussion board.

    - Posting your chart (5)

    - A brief description of your chart (5)

        - Answer:
