---
title: "Project Update 4"
subtitle: "ECON 345"
author: "Your Name"
date: "Due: 11:59PM October 10, 2026"
output: pdf_document
urlcolor: blue
---

**If your project has weights, do Parts A, C, and D only. If your project does not have weights, do Parts B, C, and D only.**

# Part A - Incorporating Weights (80 points)

1. For your summary statistics (30 points):

```{r, eval = TRUE, echo = FALSE}
# compute weighted summary statistics

```

2. Histograms (30 points):

```{r, eval = TRUE, echo = FALSE}
# compute weighted histograms

```

3. Conditional summary statistics (20 points):

```{r, eval = TRUE, echo = FALSE}
# compute weighted conditional summary statistics

```

4. Conditional histograms (20 points):

```{r, eval = TRUE, echo = FALSE}
# compute weighted conditional histograms

```

# Part B - Incorporating Feedback (80 points)

1. State all the feedback from your adviser and buddy that you have received up to this point. (30 points)
2. Incorporate the feedback you have received from your adviser and buddy. (30 points)

```{r, eval = TRUE, echo = FALSE}
# reproduce or compute results if necessary

```

3. Take previous visuals, statistics, or charts and polish them. (20 points)

```{r, eval = TRUE, echo = FALSE}
# polish previous analysis

```

# Part C - Follow-up With Your Adviser (10 points)

1. Email your adviser with the knitted output (i.e., the PDF or Word document that results from your RMD). Do not send them your R script file or your RMD, but do submit these on Canvas. In your email, give your adviser a brief summary of what you've done this week and what you've learned about your research question, and include any questions or ideas about where to take your analysis next.

    - **Email your knitted output to your adviser with econ345.spelman@gmail.com cc'd.**
    - **Continue the conversation with your adviser by summarizing your findings and brainstorming next steps in the body of your email.**

# Part D - Share With Your Classmates (10 points)

1. Please post on the Canvas discussion board for the project a post that includes:

    - **Your research topic and a brief description of your data** (5 points)
    - **A description of some of the challenges you've encountered so far** (5 points)

You're strongly encouraged to comment on your classmates' posts as well!
