---
title: "Project Update 6"
subtitle: "ECON 345"
author: "Your Name"
date: "Due: 11:59PM October 31, 2026"
output: pdf_document
urlcolor: blue
---

**For Part A, you need to reproduce your work from Project Update 5 with revisions based on feedback you received. If you did not receive any feedback for a particular item, you should still include that item.**

# Part A - Iterating on Previous Work (30 points)

1. **Research Question (10)**

    - What is your research question? (2)

        - Answer:

    - How has your research question changed over the course of the project? (2)

        - Answer:

    - What are the key relationships in your data that could inform the answer to your research question? (2)

        - Answer:

    - Based on your data, what is a testable hypothesis for your research question? (4)

        - Answer:

2. **Summary Statistics (4)**

```{r, eval = TRUE, echo = FALSE}
# generate summary statistics, incorporating weights if applicable, using vtable or kable

```

    - Feedback incorporated, or struggles/no feedback to report: (2)

        - Answer:

3. **Conditional Summary Statistics (4)**

```{r, eval = TRUE, echo = FALSE}
# generate conditional summary statistics, incorporating weights if applicable, using vtable or kable

```

    - Feedback incorporated, or struggles/no feedback to report: (2)

        - Answer:

4. **Data Visualization (12)**

```{r, eval = TRUE, echo = FALSE}
# chart 1

# chart 2

# chart 3

```

    - What story does each chart tell? (5)

        - Answer:

    - Feedback incorporated, or struggles/no feedback to report: (2)

        - Answer:

# Part B - Refining Your Interpretation (30 points)

5. What did you originally expect to find in the data about the relationship between your key variables? (5)

    - Answer:

6. How have your findings differed from your original expectations? (5)

    - Answer:

7. How does your analysis thus far help inform your research question? Tell us a story. (10)

    - Answer:

8. What limitations exist to your analysis and visualizations so far? How could you overcome these limitations? (10)

    - Answer:

# Part C - Analysis With a Simple Regression (20 points)

9. Define your dependent variable and one explanatory variable for a simple regression. Explain your reasoning. (5)

    - Answer:

10. State the null and alternative hypotheses for the slope on your explanatory variable. (5)

    - Answer:

11. Fit the regression with `lm()`, and display the results with `broom::tidy()` and `broom::glance()`. Do not use `summary()` or pull coefficients with `$`. (5)

```{r, eval = TRUE, echo = FALSE}
# library(broom)
# my_model <- lm(dependent_var ~ explanatory_var, data = your_data)
# tidy(my_model)
# glance(my_model)

```

12. Interpret the results, and visualize the relationship with a scatterplot and the fitted line from `broom::augment()`. (5)

```{r, eval = TRUE, echo = FALSE}
# augment(my_model) %>%
#   ggplot(aes(x = explanatory_var, y = dependent_var)) +
#   geom_point() +
#   geom_line(aes(y = .fitted))

```

    - Interpretation (coefficient, statistical significance, economic significance):

        - Answer:

# Part D - Follow-up With Your Adviser (10 points)

13. Email your adviser with your knitted output, with `econ345.spelman@gmail.com` cc'd. (5)

    - Summary of what you've done this week and what you've learned: (5)

        - Answer:

# Part E - Share With Your Classmates (10 points)

14. Pick one chart from Part A and share it on the Canvas discussion board.

    - Posting your chart (5)

    - A brief description of your chart (5)

        - Answer:
